A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$

### 2025-04-08 paper_v02/article.tex
tests page link

The codes used for testing are available in \url{replace}, as jupyter noteooks, in  and can easily be tested in Google colab environment. The basic version is available in \pkg{Zebende} version $0.1.91$ and the optimized implementation in version $0.2.0$ of the package.

>>>>

The basic version is available in \pkg{Zebende} version $0.1.91$ and the optimized implementation in version $0.2.0$ of the package. The codes used for testing are available, as jupyter noteooks, in the link below, where they can be tested in Google colab environment:

\begin{center}
  \url{https://255ribeiro.github.io/paper_zebendelib/notebooks/test_nb.html}
\end{center}
